Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
tries to do some rearranging into Methods vs. Model

The model is implemented using the \gls{MOOSE} \cite{gaston_physics-based_2015} application code
Moltres \cite{lindsay_arfc/moltres_nodate}. Building on the massively
parallelizable \gls{MOOSE} framework allows Moltres to be run on super-computing
platforms like \gls{NCSA}'s Blue Waters. For some three-dimensional simulations
(results not discussed here), the number of elements in the mesh and total
number of degrees of freedom exceed one million and ten million respectively. To
handle problems of this size, Moltres has been run on up to 608 cores. However,
reducing the problem dimension from three to two and using a structured mesh
that can be much more coarse in the axial direction allows problem solution to
be carried out on a single core in under five minutes.

@@

@@

\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet.

>>>>

Moltres \cite{lindsay_arfc/moltres_nodate} is implemented as an application for 
use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework.

@@

\subsection{Performance}

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres 
to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some 
three-dimensional simulations (results not discussed here), the number of 
elements in the mesh and total number of degrees of freedom exceed one million 
and ten million respectively. To handle problems of this size, Moltres has been 
run on up to 608 cores. However, reducing the problem dimension from three to 
two and using a structured mesh that can be much more coarse in the axial 
direction allows problem solution to be carried out on a single core in under 
five minutes.

@@

\cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet.
